Stay in shape! Homework exam II

### 2016-03-24 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
threw away special constraint idea

\documentclass{article}
\usepackage{amsmath}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pst-solides3d}
\usepackage{auto-pst-pdf}
\usepackage{tikz}
\usepackage{enumerate}
\renewcommand{\thesubsection}{\thesection.\alph{subsection}}
\begin{document}
\author{Jappie Klooster}
\title{Stay in shape! Homework exam II}
\maketitle
\section{A disk and some half-planes}
\subsection{Per case, what can you say about $H$}
We number the half-planes of $H$: $h_1, h_2,\dots,h_i$.
Let $H_{i}$ be the set of the first $i$ constraints with special constraints
$x_1$ and $x_2$ both one unit away from the x axis and pointing to the x
axis, and
let $C_{i}$ be the feasible region defined by these constranits:

\[ H_i := \{x_1, x_2, h_1, h_2,\dots, h_i\}\]
\[ C_i := x_1 \cap x_2 \cap h_1 \cap h_2 \cap \dots \cap h_i\]

@@

	The intersection $C_i$ is empty.

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pst-solides3d}
\usepackage{auto-pst-pdf}
\usepackage{tikz}
\usepackage{enumerate}
\renewcommand{\thesubsection}{\thesection.\alph{subsection}}
\begin{document}
\author{Jappie Klooster}
\title{Stay in shape! Homework exam II}
\maketitle
\section{A disk and some half-planes}
\subsection{Per case, what can you say about $H$}
We number the half-planes of $H$: $h_1, h_2,\dots,h_i$.
Let $H_{i}$ be the set of the first $i$ constraints, and
let $C_{i}$ be the feasible region defined by these constranits:

\[ H_i := \{h_1, h_2,\dots, h_i\}\]
\[ C_i := h_1 \cap h_2 \cap \dots \cap h_i\]

@@

		$C_i$ never crosses the x axis,
		so it exists entirely above or below $y=0$. Or the intersection is empty.
